HTW Modeling

### 2024-03-22 Analysis/e1.qmd
add e2 and e3 modeling

Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant. See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition. This difference is depicted visually in @fig-e1-test-vx.

>>>>

Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant. See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition. This difference is depicted visually in @fig-e1-test-vx.

### 2024-03-22 Model/htw_model.qmd
add e2 and e3 modeling

---
title: HTW Modeling 
author: Thomas Gorman
#date:  #"`r Sys.Date()`"
page-layout: full
categories: [Modeling, ALM, EXAM, R]
lightbox: true
toc: false
format-links: false
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e1-hugo.md
  gfm:
    echo: true
    output-file: e1-gfm.md
prefer-html: true
---

```{r}
pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
               stringr,future,furrr, knitr, reactable, flextable,ggstance, htmltools,ggdist,ggh4x)
#conflict_prefer_all("dplyr", quiet = TRUE)
walk(c("flextable","dplyr"), conflict_prefer_all, quiet = TRUE)
#options(brms.backend="cmdstanr",mc.cores=4)
options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data"), ~source(here::here(paste0("Functions/", .x, ".R"))))

@@

For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution. Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant. Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs. To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.

@@

@@

@@

# pmod1 <- post_dat_l |> filter(!(Resp=="Observed")) |> 
#   group_by(id,condit, Fit_Method,Resp,x) |> 
#  summarize(vx=mean(val)) |> 
#  left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
#   ggplot(aes(x=condit,y=vx, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
#   stat_bar + 
#     scale_color_manual(values = c("black" = "black"), guide = FALSE) +
#   scale_size_manual(values = c("black" = .5), guide = FALSE) +
#     ggh4x::facet_nested_wrap(~Resp+rename_fm(Fit_Method), axes = "all",ncol=3,scale="free") + 
#   theme(legend.position = "none",plot.title = element_text(hjust=.55) ) + labs(title="Model Predictions", y="vx", x="Condition")

pmod1 <- post_dat_l |> filter(!(Resp=="Observed")) |> 
  group_by(id,condit, Fit_Method,Resp,x) |> 
 summarize(vx=median(val)) |> 
 left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
 ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = FALSE) +
  scale_size_manual(values = c("black" = .5), guide = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions - Experiment 1 Data", y="vx")

@@

@@

pmod1 <- post_dat_l |> filter(!(Resp=="Observed")) |> 
  left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
  group_by(id,condit, Fit_Method,Resp,vb,bandType) |> 
 summarize(dist=median(dist)) |> 
 ggplot( aes(x=condit,y=dist, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = FALSE) +
  scale_size_manual(values = c("black" = .5), guide = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",
         plot.title = element_text(hjust=.50),
         plot.margin = unit(c(20,0,0,0), "pt"),
         axis.title.x = element_blank()) + 
         labs(title="Model Predictions - Experiment 1 Data", y="Deviation from target band")

@@

>>>>

---
title: HTW Modeling 
author: Thomas Gorman
#date:  #"`r Sys.Date()`"
page-layout: full
categories: [Modeling, ALM, EXAM, R]
lightbox: true
toc: false
format-links: false
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e1-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
prefer-html: true
---

```{r}
pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
               stringr,future,furrr, knitr, reactable, flextable,ggstance, htmltools,ggdist,ggh4x)
#conflict_prefer_all("dplyr", quiet = TRUE)
walk(c("flextable","dplyr"), conflict_prefer_all, quiet = TRUE)
#options(brms.backend="cmdstanr",mc.cores=4)
options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))

@@

For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution. Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant. Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs. To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.a

@@

# post_tabs$agg_pred_full_bt |> 
#    pander::pandoc.table(style="rmarkdown", split.table=Inf)
#   
# post_tabs$agg_pred_full |> 
#    pander::pandoc.table(style="rmarkdown", split.table=Inf)
# 
# post_tabs$agg_x_full_bt |> filter((Fit_Method=="Test_Train")) |>
#   mutate(Fit_Method=(Fit_Method)) |>
#   rename("Band"=x, "Condition"=condit, "Model Error"=mean_error) |>
#   pander::pandoc.table(style="rmarkdown", split.table=Inf)

@@

```{r}

library(brms)
options(brms.backend="cmdstanr",mc.cores=4)

# pdl <- post_dat_l |> rename("bandInt"=x) |> #left_join(testAvgE1,by=c("id","condit","bandInt")) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
e1_ee_brm_ae <- brm(data=pdl,
  aerror ~  Model * condit + (1+bandInt|id), 
  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

bct <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(bct) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

bct <- bct |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |>
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)

#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))

p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error")
p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

p1 + p2+ p3

bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")

posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
  select(starts_with("b_")) %>%
  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))

constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
comparison_EXAM <- constant_EXAM - varied_EXAM
summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
#print(summary_EXAM)

# alternative emmeans approach to assess constant vs. varied difference in EXAM
#emmeans(e1_ee_brm_ae, specs = "condit", by = "Model") |> summary()
# is the difference significant for EXAM in particular

To quantitatively assess whether ALM or EXAM did significantly better, and to see whether if the fits of the two models varied between Constant and Varied subjects, we fit a bayesian regressions predicting the error of the model predictions as a function of the Model (ALM vs. EXAM) and training condition (Constant vs. Varied). As is shown in @tbl-ee-brms1, the model error was significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM, and for the Varied condition  than the Constant condition ($\beta$ = `r bm2$estimate`, 95% CrI \[`r bm2$conf.low`, `r bm2$conf.high`\], pd = `r bm2$pd`). There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the difference in model error between ALM and EXAM was significantly greater for the constant condition. To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM. The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).

::: {#tbl-ee-brms1}
|Term                   | Estimate| 95% CrI Lower| 95% CrI Upper| pd|
|:----------------------|--------:|-------------:|-------------:|--:|
|Intercept              |    176.3|         156.9|         194.6|  1|
|ModelEXAM              |    -88.4|        -104.5|         -71.8|  1|
|conditVaried           |    -37.5|         -60.4|         -14.2|  1|
|ModelEXAM:conditVaried |     60.4|          36.2|          83.8|  1|

Comparison of model errors - experiment 1 - assessed bayesian regression in the form of Model Error ~ Model * Condition. The intercept reflects the baseline of ALM and Constant. The other estimates indicate deviations from the baseline for the EXAM mode and varied condition. {.striped .hover .sm}
:::

@@

pmod1 <- post_dat_l |> filter(!(Resp=="Observed")) |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
 summarize(vx=median(val)) |> 
 #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
 ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions - Experiment 1 Data", y="vx")

@@

::: {#tbl-model-pred1}

|  condit  | Fit_Method |  x   |   bandType    |  ALM  | EXAM  | Observed |
|:--------:|:----------:|:----:|:-------------:|:-----:|:-----:|:--------:|
| Constant | Test_Train | 100  | Extrapolation | 462.6 |  400  |  491.8   |
| Constant | Test_Train | 350  | Extrapolation | 883.9 | 581.8 |  644.7   |
| Constant | Test_Train | 600  | Extrapolation | 903.7 | 774.7 |  759.7   |
| Constant | Test_Train | 800  |    Trained    | 903.7 | 924.4 |  967.2   |
| Constant | Test_Train | 1000 | Extrapolation | 903.7 | 1064  |   1164   |
| Constant | Test_Train | 1200 | Extrapolation | 898.9 | 1197  |   1241   |
|  Varied  | Test_Train | 100  | Extrapolation | 592.3 | 569.5 |  544.4   |
|  Varied  | Test_Train | 350  | Extrapolation | 861.9 | 703.5 |  696.6   |
|  Varied  | Test_Train | 600  | Extrapolation | 918.1 | 843.8 |  830.2   |
|  Varied  | Test_Train | 800  |    Trained    | 940.9 | 945.3 |   1075   |
|  Varied  | Test_Train | 1000 |    Trained    | 1014  | 1044  |   1166   |
|  Varied  | Test_Train | 1200 |    Trained    | 1031  | 1042  |   1295   |

Model predictions experiment 1 -  empirically observed values and predictions of ALM and EXAM for each band (x) and bandType (Trained vs. Extrapolation) {.striped .hover .sm}
:::

@@

pmod1 <- post_dat_l |> filter(!(Resp=="Observed")) |> 
  #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
  group_by(id,condit, Fit_Method,Resp,vb,bandType) |> 
 summarize(dist=median(dist)) |> 
 ggplot( aes(x=condit,y=dist, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = FALSE) +
  scale_size_manual(values = c("black" = .5), guide = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",
         plot.title = element_text(hjust=.50),
         plot.margin = unit(c(20,0,0,0), "pt"),
         axis.title.x = element_blank()) + 
         labs(title="Model Predictions - Experiment 1 Data", y="Deviation from target band")

@@

```{r}
#| fig-height: 11
#| fig-width: 11

e2_model <- load_e2()
post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)

pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

rbind(post_tabs2$agg_pred_full |> mutate(stage="Test"), train_tab2$agg_pred_full |> mutate(stage="Train")) |> 
  mutate(Fit_Method=rename_fm(Fit_Method)) |>
  flextable::tabulator(rows=c("stage","Fit_Method","Model"), columns=c("condit"),
                       `ME` = as_paragraph(mean_error)) |> as_flextable()

e2_ee_brm_ae <- brm(data=pdl2,
  aerror ~  Model * condit + (1+bandInt|id), 
  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

bct <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(bct) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

bct <- bct |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |>
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)

#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))

p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error")
p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

 p1 + p2+ p3

bm1 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
bm2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
bm3 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")

```{r}

pemp2 <- e2 |> filter(expMode2=="Test") |> mutate(Resp="Observed") |> 
  ggplot(aes(x=condit,y=vx, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar+ 
  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
  theme(legend.position="right", axis.title.x = element_blank(), plot.title = element_text(hjust=.50)) +
  labs(title="Empirical Data - Experiment 1",y="vx", x="Condition",fill="Band")

pmod2 <- e2_model$post_dat_l |> filter(!(Resp=="Observed")) |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
 summarize(vx=median(val)) |> 
 ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~Resp+rename_fm(Fit_Method), strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions - Experiment 1 Data", y="vx")

(pemp2)  / pmod2 + 
  plot_layout(design = layout, heights = unit(c(4, 9), c('cm','null')))
```

```{r}

e3_model <- load_e3()
post_tabs3 <- abc_tables(e2_model$post_dat,e3_model$post_dat_l)
train_tab3 <- abc_train_tables(e2_model$pd_train,e3_model$pd_train_l)

pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

rbind(post_tabs3$agg_pred_full |> mutate(stage="Test"), train_tab3$agg_pred_full |> mutate(stage="Train")) |> 
  mutate(Fit_Method=rename_fm(Fit_Method)) |>
  flextable::tabulator(rows=c("stage","Fit_Method","Model"), columns=c("condit"),
                       `ME` = as_paragraph(mean_error)) |> as_flextable()

# e3_ee_brm_ae <- brm(data=pdl3,
#   aerror ~  Model * condit+ (1+bandInt|id) + (1+condit|bandOrder), 
#   file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint.rds")),
#   chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

e3_ee_brm_ae <- brm(data=pdl3,
  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

bct <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(bct) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

bct <- bct |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  tibble::remove_rownames() |>
  mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)

#wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))

plot(conditional_effects(e3_ee_brm_ae, 
                         effects = "Model:condit", 
                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
     points=FALSE,plot=TRUE)

p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error")
p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

 p1 + p2+ p3

bm1 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
bm2 <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
bm3 <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
